%%%%
% MTecknology's Resume
%%%%
% Author: Vaibhav Adsare
% License: CC-BY-4
% - https://creativecommons.org/licenses/by/4.0/legalcode.txt
%%%%

\documentclass[letterpaper,10pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
%% NOTE: Everything between here and END_FILE can
%% be relocated to "mteck.sty" and then included with:
%\usepackage{mteck}

% Dependencies
% NOTE: Some packages (lastpage, hyperref) require second build!
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}

% Sans-Serif
%\usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
%\usepackage[sfdefault]{noto-sans}
%\usepackage[default]{sourcesanspro}

% Serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% Colors
% Use with \color{Name}
% Can wrap entire heading with {\color{accent} [...] }
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

%-----------------%
% Custom Commands %
%-----------------%

% Centered title along with subtitle between HR
% Usage: \documentTitle{Name}{Details}
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    %{\footnotesize\color{accentTitle} #2}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

% Create a footer with correct padding
% Usage: \documentFooter{\thepage of X}
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

% Simple wrapper to set up page numbering
% Usage: \numberedPages
% WARNING: Must run pdflatex twice!
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

% Section heading with horizontal rule
% Usage: \section{Title}
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

% Section heading with separator and content on same line
% Usage: \tinysection{Title}
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

% Indented line with arguments left/right aligned in document
% Usage: \heading{Left}{Right}
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

% Adds \textbf to \heading
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

% Adds \textit to \heading
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

% Template for itemized lists
% Usage: \begin{resume_list} [items] \end{resume_list}
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
  %\vspace{-2pt}
}

% Formats an item to use as an itemized title
% Usage: \itemTitle{Title}
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{2pt}
}

% Bullets used in itemized lists
\renewcommand\labelitemi{--}

%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%


%===================%
% John Doe's Resume %
%===================%

%\numberedPages % NOTE: lastpage requires a second build
%\documentFooter{\thepage of 2} % Does similar without using lastpage
\begin{document}

   %---------%
  % Heading %
  %---------%

  \documentTitle{VAIBHAV ADSARE}{
    % Web Version
    %\raisebox{-0.05\height} \faPhone\ [redacted - web copy] ~
    %\raisebox{-0.15\height} \faEnvelope\ [redacted - web copy] ~
    %%
    \href{tel:1234567890}{
      \raisebox{-0.05\height} \faPhone\ +91 8575406800} ~ | ~
    \href{mailto:user@domain.tld}{
      \raisebox{-0.15\height} \faEnvelope\ vaibhavadsare3333@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/vaibhav-adsare-b00a96237}{
      \raisebox{-0.15\height} \faLinkedin\ linkedin.com/in/vaibhav-adsare-b00a96237} ~ | ~
    \href{https://github.com/Vaibhav-09032002}{
      \raisebox{-0.15\height} \faGithub\ github.com/Vaibhav-09032002}
  }

  %---------%
  % Summary %
  %---------%

  \tinysection{Summary}
  Detail-oriented team player with strong organizational skills. Ability to handle multiple projects simultaneously with a high degree of accuracy. Seeking a full-time position that offers professional challenges utilizing interpersonal skills, excellent time management, and problem-solving skills.

  %--------%
  % Skills %
  %--------%

 \section{Skills}

\begin{description}[leftmargin=*, style=unboxed, itemsep=-2px, parsep=1pt]
  \item[\textbf{Languages :}] C, Java, JavaScript, SQL
  \item[\textbf{Web Development :}] HTML, CSS
  \item[\textbf{Software Tools :}] VS code, Git  \& Github, Figma
  \item[\textbf{Computer Science Fundamentals:}] Operating Systems, OOP, Data Structures and Algorithms (DSA), DBMS.
\end{description}




  %------------%
  % Experience %
  %------------%

  \section*{Projects}

\subsection*{Drain Block Test Jig (Internship Project)}
\begin{itemize}
    \item Designed and implemented the Drain Block Test Jig to evaluate the drainage system efficiency of refrigerators.
    \item Collaborated with cross-functional teams to integrate the jig seamlessly into the product testing workflow.
    \item Developed a user-friendly and cost-effective solution for identifying drainage blockages.
    \item Contributed to improved product reliability and reduced maintenance costs.
\end{itemize}

\subsection*{Integrating IoT Cloud Technology for Control and Monitoring of Sensors}
\begin{itemize}
    \item Developed a project to leverage cloud-based IoT solutions for managing and observing sensor networks.
    \item Utilized DHT11 sensors for temperature and humidity measurement.
    \item Implemented IR sensors for motion detection.
    \item Integrated the ESP8266 module for Wi-Fi connectivity to enable communication with the cloud.
    \item Enabled real-time data collection, remote control, and automated monitoring through cloud integration.
\end{itemize}

\subsection*{Netflix Clone(Front End Website)}
\begin{itemize}
     \item Developed a Netflix clone focusing on front-end design using HTML and CSS.
    \item Created a responsive user interface to replicate Netflix's modern design and user experience.
    \item Utilized CSS for layout, media queries for responsiveness, and custom styling to mirror Netflix's layout.
    \item Optimized the website for different screen sizes and devices, ensuring a seamless viewing experience across platforms.
\end{itemize}


  %-----------%
  % Education %
  %-----------%

  \section{Education}

  \headingBf{Bachelor of Technology in Electronics and Telecommunication (8.99 CGPA)}{} % Note: Adding year(s) exposes an implied age
  \headingIt{Vishwakarma Institute Of Information Techonology,Pune [2020-2024]}{}

  \headingBf{Higher Secondary Certification
 Examination (74.14 percent)}{} % Note: Adding year(s) exposes an implied age
  \headingIt{Janata Junior College,MH[2020]}{}

 \headingBf{Secondary School Certification
 Examination (89 percent)}{} % Note: Adding year(s) exposes an implied age
  \headingIt{Vidyadham Prashala,Shirur[2018]}{}


  %----------------------------%
  % Extracurricular Activities %
  %----------------------------%

  \section{Experience}

  \subsection*{Intern - Trainee Engineer}
\textbf{Global Calibration} \hfill \textit{07/2023 - 12/2023, Pune}

\begin{itemize}[itemsep=1pt, parsep=1pt]
    \item Contributed to core electronics projects for LG Electronics and Voltas during my internship at Global Calibration.
    \item Designed jigs to improve efficiency and precision in calibration methodologies.
    \item Gained hands-on experience in electronics calibration processes and specialized tool creation.
\end{itemize}

\end{document}